WHAM MSE startup

### 2025-04-07 GettingStarted.Rmd
start pages

@@

```{r}
nsim <- 100 
set.seed(8675309) 
sim_input <- list()
sim_input <- lapply(1:nsim, function(x) {
  input_i <- om$input
  sim <- om$simulate(complete=TRUE)
  input_i$data <- sim
  return(input_i)
})

@@

@@

SSB <- lapply(1:nsim, function(x){
  SSB_est <- sim_fits[[x]]$rep$SSB
  SSB_true <- sim_fits[[x]]$input$data$SSB
  SSB <- cbind(SSB_est, SSB_true)
  return(SSB)
})
print(SSB)
```

>>>>

```{r}
library(wham)
library(whamMSE)

main.dir = here::here()
```

@@

Self test, run once, took 6 hours

```{r, eval=FALSE}
nsim <- 100 
set.seed(8675309) 
sim_input <- list()
sim_input <- lapply(1:nsim, function(x) {
  input_i <- om$input
  sim <- om$simulate(complete=TRUE)
  input_i$data <- sim
  return(input_i)
})

@@

#skg added
saveRDS(sim_fits, here::here("localhugefiles/sim_fits_self_test.rds"))

@@

SSB <- lapply(1:nsim, function(x){
  SSB_est <- sim_fits[[x]]$rep$SSB
  SSB_true <- sim_fits[[x]]$input$data$SSB
  SSB <- cbind(SSB_est, SSB_true)
  return(SSB)
})
print(SSB)

```

What does the object look like? Huge

```{r}
sim_fits <- readRDS(here::here("localhugefiles/sim_fits_self_test.rds"))

```
